\section{Related Work}
\label{sec:related_work}

\para{Subspace-based representation comparison.} Early work on neural representation similarity focused on subspace alignment. \svcca removes low-variance directions and then applies canonical correlation analysis to compare hidden representations across layers, checkpoints, and models \cite{raghu2017svcca}. \pwcca extends this line by reweighting canonical directions according to their contribution to the representation, which can make the score better reflect dominant activation structure. These methods are natural starting points for our setting because they compare whole hidden spaces rather than individual neurons. Our study uses both \svcca and \pwcca, but evaluates them in a simple MLP regime where architecture and training are tightly controlled.

\para{Kernel-style similarity and metric reliability.} \citet{kornblith2019similarity} argued that linear \cka is often more reliable than CCA-style measures for high-dimensional correspondence tests, making it a strong default baseline for layer-by-layer analysis. At the same time, later work showed that no single geometric metric is sufficient. \citet{davari2023reliability} demonstrated that \cka can be sensitive to outliers and certain feature transformations even when downstream usefulness is preserved. The broader survey of \citet{klabunde2023survey} makes the same point at a higher level: different similarity scores encode different invariances and answer different scientific questions. We follow this guidance directly by reporting four metrics rather than relying on one preferred score.

\para{Functional compatibility and decodable information.} Geometric similarity is not the same as functional interchangeability. Model stitching work showed that representations can be functionally compatible even when their geometric similarity is modest \cite{csiszarik2021similarity}. More recent theoretical work linked common similarity measures to alignment between optimal linear readouts, clarifying when geometric agreement should imply agreement in decodable information \cite{harvey2024decodable}. Recent layer-wise analyses also report that nearby layers tend to be more similar than distant ones, especially in larger modern architectures \cite{jiang2024tracing}. Our paper positions itself as a controlled benchmark for plain MLPs that brings these threads together: we measure geometry with multiple metrics, test layer recurrence across seeds, and add linear probes to track task information by depth.
